Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-26 paper.qmd
Figure 18 changed the colors

highd_error_2d_mnist <- error_df |>
  ggplot(aes(x = tSNE1,
             y = tSNE2,
             colour = sqrt_row_wise_abs_error)) +
  geom_point(alpha=0.2) +
  scale_colour_continuous_sequential(palette = "Light Grays") +
  geom_rect(aes(xmin = 0.8, xmax = 0.9, ymin = 0.45, ymax = 0.6),
               fill = "transparent", color = "#e41a1c", linewidth = 0.7) +
  geom_rect(aes(xmin = 0.75, xmax = 0.85, ymin = 0.8, ymax = 0.95),
               fill = "transparent", color = "#377eb8", linewidth = 0.7)  +
  geom_rect(aes(xmin = 0.45, xmax = 0.55, ymin = 0.45, ymax = 0.6),
               fill = "transparent", color = "#4daf4a", linewidth = 0.7)  +
  geom_rect(aes(xmin = 0.7, xmax = 0.8, ymin = 0.25, ymax = 0.4),
               fill = "transparent", color = "#984ea3", linewidth = 0.7) 
  # scale_colour_brewer(
  #   type = "seq",
  #   palette = 1
  # ) #+ 
  # theme(
  #     legend.position = "bottom",
  #     legend.text = element_text(size = 10),          # Increase legend text size
  #     legend.key.size = unit(1, "lines")              # Increase size of legend keys
  # ) +
  # guides(
  #     color = guide_legend(
  #         override.aes = list(size = 2.5, alpha = 1)      # Increase point size and opacity in legend
  #     )
  # ) 
```

@@

right_top_img <- pixels_gathered_within |>
  ggplot(aes(x, y, fill = value)) +
  geom_tile() +
  facet_wrap(~ instance, ncol = 4) +
  coord_fixed() +
  scale_fill_continuous_sequential(palette = "Blues 3") +
  theme(strip.background = element_blank(),
        strip.text.x = element_blank(),
        legend.position = "none")

@@

imge_error_sample_outside <- pixels_gathered_outside |>
  ggplot(aes(x, y, fill = value)) +
  geom_tile() +
  facet_wrap(~ instance, ncol = 4) +
  coord_fixed() +
  scale_fill_continuous_sequential(palette = "Reds 2") +
  theme(strip.background = element_blank(),
        strip.text.x = element_blank(),
        legend.position = "none")

>>>>

highd_error_2d_mnist <- error_df |>
  ggplot(aes(x = tSNE1,
             y = tSNE2,
             colour = sqrt_row_wise_abs_error)) +
  geom_point(alpha=0.2) +
  scale_colour_continuous_sequential(palette = "Blues") +
  geom_rect(aes(xmin = 0.8, xmax = 0.9, ymin = 0.45, ymax = 0.6),
               fill = "transparent", color = "#000000", linewidth = 0.7) +
  geom_rect(aes(xmin = 0.75, xmax = 0.85, ymin = 0.8, ymax = 0.95),
               fill = "transparent", color = "#e41a1c", linewidth = 0.7)  +
  geom_rect(aes(xmin = 0.45, xmax = 0.55, ymin = 0.45, ymax = 0.6),
               fill = "transparent", color = "#4daf4a", linewidth = 0.7)  +
  geom_rect(aes(xmin = 0.7, xmax = 0.8, ymin = 0.25, ymax = 0.4),
               fill = "transparent", color = "#984ea3", linewidth = 0.7) 
  # scale_colour_brewer(
  #   type = "seq",
  #   palette = 1
  # ) #+ 
  # theme(
  #     legend.position = "bottom",
  #     legend.text = element_text(size = 10),          # Increase legend text size
  #     legend.key.size = unit(1, "lines")              # Increase size of legend keys
  # ) +
  # guides(
  #     color = guide_legend(
  #         override.aes = list(size = 2.5, alpha = 1)      # Increase point size and opacity in legend
  #     )
  # ) 
```

@@

right_top_img <- pixels_gathered_within |>
  ggplot(aes(x, y, fill = value)) +
  geom_tile() +
  facet_wrap(~ instance, ncol = 4) +
  coord_fixed() +
  scale_fill_continuous_sequential(palette = "Reds 2") +
  theme(strip.background = element_blank(),
        strip.text.x = element_blank(),
        legend.position = "none")

@@

imge_error_sample_outside <- pixels_gathered_outside |>
  ggplot(aes(x, y, fill = value)) +
  geom_tile() +
  facet_wrap(~ instance, ncol = 4) +
  coord_fixed() +
  scale_fill_continuous_sequential(palette = "Grays") +
  theme(strip.background = element_blank(),
        strip.text.x = element_blank(),
        legend.position = "none")
